Duplicate Question Detection using Online Learning

### 2016-10-23 paper/main.tex
update papers

Comparing with previous studies, we are aiming to demonstrate how these techniques can be used in an online learning context. Online learning focuses on modelling data which arrives in sequential order to update our best predictor for future data as opposed to training on the whole training data set at once. This is important part of this project as with young communities, often the whole training data set will not be available until the community is relatively mature. Pal \emph{et al.}\cite{pal} explains that early identification and engagement with these users  can improve the experience of these users and more importantly improve the overall quality of participation within a community. Within Pal \emph{et al.}\cite{pal} retrospective analysis, it had already shown that some of the potential experts had already left the community when the analysis concluded leading to missed opportunities within the community.

@@

Having adaptive duplication detection not only assists in special events but also in young communities, where there is a lack of training data or examples to create a sensible detection for duplicated questions. On forums like Piazza this would assist in reducing the amount of clutter which exists, similar to how stackoverflow closes duplicate questions for redundant questions to decrease the maintenance and people's resources on answering the same question.

@@

Based on synthetic, Piazza, Google plus.

@@

Which one to use and why?

@@

>>>>

Comparing with previous studies, we are aiming to demonstrate how these techniques can be used in an online learning context. Online learning focuses on modelling data which arrives in sequential order to update our best predictor for future data as opposed to training on the whole training data set at once. This is important part of this project as with young communities, often the whole training data set will not be available until the community is relatively mature. This research would be similar to Zhang \emph{et al}\cite{dupred} conducted similar experiment with duplicate question detection via batch learning. Pal \emph{et al.}\cite{pal} explains that early identification and engagement with these users  can improve the experience of these users and more importantly improve the overall quality of participation within a community. Within Pal \emph{et al.}\cite{pal} retrospective analysis, it had already shown that some of the potential experts had already left the community when the analysis concluded leading to missed opportunities within the community.

@@

Having adaptive duplication detection not only assists in special events but also in young communities, where there is a lack of training data or examples to create a sensible detection for duplicated questions. On forums like Piazza this would assist in reducing the amount of clutter which exists, similar to how stackoverflow closes duplicate questions for redundant questions to decrease the maintenance and people's resources on answering the same question\cite{dupred}.

@@

Our online learning model is evaluated on historical questions in Stack Overflow. We parse data for `html' and `javascript' tags from January 2008 to October 2016 using Stackexchange API. We extract approximately 750 000 questions over 10 month period.

A Python library called Gensim was used to extract fields from the questions. Gensim is a flexible Python library statistical semantics.

@@

To evaluate the performace, we will use recall-rate which is also used in \cite{dupred}

$$
\text{recall-rate} = \frac{N_\text{detected}}{N_\text{total}}
$$

@@

Zhang \emph{et al}\cite{dupred}
